SunPy - Python for Solar Physics

### 2014-01-26 4-Util.tex
more edits to util.

\subsubsection{Sun}
The purpose of this module is to provide solar-specific data for example ephemeris and
solar constants. The main namespace contains a number of functions which provide solar
ephemeris such as the sun to earth distance, solar cycle number, the mean anomaly, etc.
All of these functions take a time as their input which can be provided in any 
parse\_time
compatible format. 
A future version of SunPy will integrate with the AstroPy coordinates package and will 
likely make use of an ephemeris package.

\subsubsection{constants}
The purpose of the constants package is to provide a number of solar-related 
constants in order to provide consistency in the calculations of derived solar 
values both within the SunPy code base but also to the user. Every solar 
constants is provided as a Constant objects as defined by Astropy. Each 
Constant object defines a Quantity, a number associated with a unit, along with 
the constant's provenance (i.e. reference) as well as its uncertainty. Using 
Astropy's Quantities, any solar constant can easily be converted between 
different units as can be seen in Figure~\ref{fig:constants_code} as well
as between SI or cgs with a single command.  As these objects inherit from 
Numpy's ndarray, they work well with standard representations of numbers.
For convenience a number of shortcuts to frequently used constants are provided 
directly when importing the sub-package. A larger list of constants can be 
accessed through an interface modelled on that provided by the SciPy constants 
package and are available as a dictionary called \texttt{physical\_constants}. 
To view them all quickly a \texttt{print\_all()} function is available.

>>>>

\subsubsection{Sun}
The purpose of this module is to provide solar-specific data for example ephemeris and
solar constants. The main namespace contains a number of functions which provide solar
ephemeris such as the sun to earth distance, solar cycle number, the mean anomaly, etc.
All of these functions take a time as their input which can be provided in any 
\texttt{parse\_time}
compatible format. 
A future version of SunPy will integrate with the AstroPy coordinates package and will 
likely make use of an ephemeris package.

\subsubsection{constants}
The purpose of the constants package is to provide a number of solar-related 
constants in order to provide consistency in the calculations of derived solar 
values both within the SunPy code base but also to the user. Every solar 
constant is provided as a Constant object as defined by Astropy. Each 
Constant object defines a Quantity, a number associated with a unit, along with 
the constant's provenance (i.e. reference) as well as its uncertainty. Using 
Astropy's Quantities, any solar constant can easily be converted between 
different units as can be seen in Figure~\ref{fig:constants_code} as well
as between the SI or cgs unit systems with a single command.  As these objects inherit from 
Numpy's ndarray, they work well with standard representations of numbers.
For convenience a number of shortcuts to frequently used constants are provided 
directly when importing the sub-package. A larger list of constants can be 
accessed through an interface modelled on that provided by the SciPy constants 
package and is available as a dictionary called \texttt{physical\_constants}. 
To view them all quickly a \texttt{print\_all()} function is available.
